GEE models

### 2017-07-01 doc/manuscript.Rmd
results agnostic title

Title: Total non-esterified fatty acids, but not individual fatty acids, predict
progression in beta-cell dysfunction: The Prospective Metabolism and Islet Cell
Evaluation (PROMISE) cohort

>>>>

Title: Association of non-esterified fatty acid composition with insulin
sensitivity and beta-cell dysfunction in the Prospective Metabolism and Islet Cell
Evaluation (PROMISE) cohort
